---
title: 'Stat355, Assignment #3, due: Friday, October 18 in class'
author: "Put your name"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  word_document: default
  html_document:
    df_print: paged
graphics: yes
indent: yes
geometry: left=1.5cm,right=1.5cm,top=2cm,bottom=3cm
fontsize: 11pt
---

## Multiple regression and Dummy Variables, Section 11.2

### Instructions:
1. Complete your assignment in R Markdown using this file as a template.
Insert R code in the R chunks, and type in your response after the
corresponding R chunk leaving one blank line between the R chunk and
your comments. 
2. Execute each line of code separately to ensure that it works properly.
3. Either [knit the entire document to pdf] or [knit to HTML or Word and print to pdf].
4. Submit the pdf file to CourseSpaces in the Assignment 3 activity.

### Data Description:
Question 11.Review.15(new book)  11.Review.17(old book)

In a study, subjects were preterm infant with low birth weights born in
three different hospitals.  The variables are:   

    WEIGHT:  weight in kg  (Y variable)  
    WEEKS:  gestation age in weeks  
    HOSP:  Hospital of birth, A, B or C  

0.  Read the data into R using the read.csv function. 
```{r OptionsReadIn}
knitr::opts_chunk$set(fig.width=8, fig.height=6) #set size of graphs
HOSPB<-read.csv('REV_C11_17.csv')
dim(HOSPB)
HOSPB$HOSPn <- as.numeric(HOSPB$HOSP)  #create a numeric HOSP for plotting
```

<header> Questions: </header>

1.  Provide descriptive statistics and a pairs plot for the data.  
Comment on your results and especially on any unusual features in the data. (3 marks)
```{r SummaryPairs}

```


2.  Provide summary statistics of the dataset by HOSP and comment.  (3 marks)
```{r byHOSP}

```


3.  Provide a scatterplot of WEIGHT versus WEEKS, using a different plotting
character and colour for each of the three hospitals.  Comment on the graph. (2 marks)
```{r Scatter}


```


4.	Fit parallel lines model for WEIGHT versus WEEKS, where the intercepts may differ
by HOSP but the slopes are the same.  Provide a summary of the model and comment. (4 marks)
```{r Parallel}

```


5.	Fit a model for WEIGHT versus WEEKS, where the intercepts and slopes may differ
by HOSP.  Provide a summary of the model and comment. (4 marks)
```{r DifSlopes}

```


6.  Provide a scatterplot of WEIGHT versus WEEKS, using a different plotting
character and colour for each of the three hospitals.  Overlay the fitted lines from
the model in Question 5. (2 marks)
```{r DifSlopesScatter}

```

7.  Compare the models in Questions 4 and 5.  Which one model would you present to your boss and why? (3 marks)











