---
title: "Assignment2 STAT 353"
author: "Zimeng Ming V00844078"
date: "2019/10/7"
output: html_document
---
<br>
<br>
Question 1 and 3 is on the paper attached.

<hr>
<b>Question2:</b>
<br>
a)
  
```{r}
gpa<-read.table("2.7.txt",header = T)

fit1<-lm(gpa$GPA~gpa$GMAT)
summary(fit1)
```

So the R_square is 0.02937
the model is GPA=2.157611+0.001931(GMAT)+e
<br>

b):
<br>
the second person fitted value is: 2.157611+0.001931(540)=3.20034 
<br>
so the estimate GPA for seconde person is: 
3.2

<br>

c):
```{r}
anova(fit1)
```


The p-value is significantly lager then 0.05, which is 0.5943, so the sigificant eveidence shows that do not reject H0:the beta1 is 0, so we can conclude that the GMAT is not an important predictor variable.

<hr>

<b>Question 4</b>
a)<br>
Assumptions:<br>
  ** x is fixed<br>
  ** E(Ei)=0<br>
  ** V(Ei)= Theata^2 which is a constant<br>
  ** cov(ei,ej)=0 for i not equal to j(Ei are independent) 

```{r}
data<-read.table("2.12.txt",header = T)


fit2<-lm(data$y~data$x)
summary(fit2)
```

So the model is y=-0.228090+0.994757x+e

b): 
```{r}
confint(fit2, level = 0.95)
```

The 95% confidence interval for the intercept(beta0) is :
(-0.5459503,0.08977054)

c): 
The 95% confidence interval for the slope of the model(beta1) is :
( 0.9827204 ,1.00679271)


d):
  i): If the x=0, y=0.228090, which is not a no calcium present. also the CI for the        intercept(beta0) contains zero, also shows there should be no corresponding           result.
  ii): As 1 is included in the confidence interval for slope(beta1), so the slope           could be 1.
  
e):
```{r}
#we need beta0 is 0 so we use the zero intercept.
fit3<-lm(data$y~0+data$x)
summary(fit3)
confint(fit3, level = 0.95)
```
Comment:
The new model line is y=0.987153x+e<br>
here the new 95% confidence interval for the slope of the model(beta1) is :
(0.9810362, 0.9932693)


f): 
As we change the model, we remove the intercept term so the slope will change either. The new CI for the beta1 is not include 1 since the model slope is change.

