---
title: "Assignment1"
author: "Zimeng Ming V00844078"
date: "2019/1/22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Question2: 

a):
```{r}
Question1_data<-read.table("Question1.txt",header = T)

Question1_data

```

b): Sort the data by plant growth

```{r}
attach(Question1_data)

Question1_data_sorted <- cbind(growth[order(Question1_data$growth)],trt[order(Question1_data$growth)],plot[order(Question1_data$growth)],pot[order(Question1_data$growth)])

Question1_data_sorted
```

c)Mean and deviation:
```{r}
print("The mean for the growth is: ")
mean(growth)

print("The Standard Deviation of the sample is :")
sqrt(var(growth))
```

d) Plot the data
```{r}
hist(growth,main="The Histogram of Plant Growth(mm)",xlab = "Growth(mm)",breaks = 10,xlim = c(5,26) )
```



Question3: 
The sum of the squares of a vector
```{r}
sum_of_squares<-function(y){
  
  y_square=0
  #using for loop to calculate the sum square of (Y[i]-mean)
  for(i in 1:length(y)){
    y_square=(y[i])^2+y_square
  }
  #using the sqyares formula.
  y_square-(length(y)*((sum(y)/length(y)))^2)
  
}

#Test the data
y<-c(11,11,10,8,11,3,15,11,7,6)
sum_of_squares(y)



```

However, for this question, I have different answers for the code using to calculate the variance. 
  sum_of_squares<-function(y){
  y_square=0
  #using for loop to calculate the sum square of (Y[i]-mean)
  for(i in 1:length(y)){
  y_square=(y[i]-mean(y))^2+y_square
  }
  #using the sqyares formula.
  y_square/(length(y)-1)
  }
  #Test the data
  y<-c(11,11,10,8,11,3,15,11,7,6)
  sum_of_squares(y)
  ## [1] 11.34444

But I do not know what is wrong with my code. I could not find a way that using the formula of sum of sequares that can get accurate variance. 






Question4:
```{r}
power.t.test(delta = 6,sd=3,sig.level = 0.05,power = 0.8,type = "one.sample")
```

so the sample size required is 5.

Question5:

```{r}
#for the function, we use n=z^2*s^2/d^2 where z is confidence interval, s is standard deviation and d is margin of error. 

Population_via_CI<-function(CI, margin_of_error,standard_deviation){
  #set the value for Confidence Interval
  z<-qt(CI,df = Inf)
  
  #set margin of error
  d<-margin_of_error
  
  #set the standard deviation
  s<-standard_deviation
  
  #calculate the population
  ((z/d)^2)*(s^2)
  
  
  
}


```


Question6:
```{r}
Population_via_CI(0.95,2,3)
```

So the answer is n=7.
